Category-Pivot Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection

### 2016-10-06 paper/lncsFormat.tex
finish sec 2.1.1.2; 5208 words (related works)(event detection).(without extra information).(word frequencies)

\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Category-Pivot Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
%构造（building）一个**词表（找一个词对它更合适的描述），for transfer learning in accurate event detection
%\title{Constructing Knowledge Base's Category Topics for Transfer Learning in Accurate Microblog Event Detection}
\maketitle

@@

Knowledge base can be a good supplementary for event detection on microblog stream.
Different from the not-well-organized microblog stream, knowledge base (e.g. Wikipedia) is constructed elaborately and contains rich information. 
For example, the microblog message ``Possible Ft. Hood Attack Thwarted (2011-07-28)'' is short, but still comprehensible because the words ``\textit{Ft. Hood}" is included in the wiki page ``\textit{Ft. Hood}", and belongs to the category ``\textit{Military}''.
By reading these two wiki pages, the model easily understands the example tweet is talking about something related to \textit{Military}.
In other words, knowledge base enriches the linkages between words, and provides more comprehensive context for microblogs.
Since the transfer learning\cite{pan2010survey} aims at utilizing the extra information restored in the source dataset to benefit the target dataset, it provides a feasible way to enhance the event detection in microblog stream.
%拆成两个小图，中间说明这是transfer learning过后的
\begin{figure}[h]
        \centering
        \includegraphics[width=1.0\columnwidth]{img/hood.pdf}
        \caption{Hood\footnote{\url{https://en.wikipedia.org/wiki/Naser_Jason_Abdo#Arrest}}\footnote{\url{https://en.wikipedia.org/wiki/Fort_Hood#2011_attack_plot}}}
        \label{fig:hood}
\end{figure}

@@

\section{Related Works}
\label{sec:relatedWorks}
\textbf{Event Detection.} According to how much data are used, the approaches are divided into two groups: the detection only without extra information, and the detection by leveraging extra information.

Most existing methods belong to the first group.
They utilize the bursty pattern in the text stream to detect events, and are implemented by  clustering articles\cite{Allan:2000wu,Petrovic:2010uj,Wurzer:2015wq}, analyzing word frequencies\cite{Mathioudakis:2010fc,Weng:2011wz}, or finding bursty topics\cite{Diao:2012wj,Yan:2015wm}. 
(1) By clustering articles, UMass\cite{Allan:2000wu}, LSH\cite{Petrovic:2010uj}, k-Term-FSD\cite{Wurzer:2015wq} and other similar methods model the occurred events as clusters of articles, and link the incoming article with an already existed event cluster or label it as the first story of a new event.
The decision is based on whether the dissimilarity between the incoming article and existed event clusters is over the user-specified threshold. 
Taking LSH as an example, as \cite{Petrovic:2010uj} discussed, the threshold controls the result: the big one leads to very few and broad clusters, while the small one results in very small and specific clusters.
Even after carefully set the appropriate threshold, the clusters generated by this kind method are still mixed of events and non-events due to large portion of non-event microblogs, which requires some post-processing methods as the supplement. 
(2) By analyzing word frequencies, 
(3) By finding bursty topics, TimeUserLDA, BurstyBTM needs the appropriate number of topics to run the topic modelling, and detects the ``large" events that associate with many articles but ignores the ``small" ones.

>>>>

\usepackage{hyperref}
\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Category-Pivot Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
%构造（building）一个**词表（找一个词对它更合适的描述），for transfer learning in accurate event detection
%\title{Constructing Knowledge Base's Category Topics for Transfer Learning in Accurate Microblog Event Detection}
\maketitle

@@

Knowledge base can be a good supplementary for event detection on microblog stream.
Different from the not-well-organized microblog stream, knowledge base (e.g. Wikipedia) is constructed elaborately and contains rich information. 
For example, the microblog message ``Possible Ft. Hood Attack Thwarted (2011-07-28)'' is short, but still comprehensible because the words ``\textit{Ft. Hood}" is included in the wiki page ``\textit{Ft. Hood}", and belongs to the category ``\textit{Military}''.
By reading these two wiki pages, the model easily understands the example tweet is talking about something related to \textit{Military}.
In other words, knowledge base enriches the linkages between words, and provides more comprehensive context for microblogs.
Since the transfer learning\cite{pan2010survey} aims at utilizing the extra information restored in the source dataset to benefit the target dataset, it provides a feasible way to enhance the event detection in microblog stream.
%拆成两个小图，中间说明这是transfer learning过后的
\begin{figure}[h]
        \centering
        \includegraphics[width=1.0\columnwidth]{img/hood.pdf}
        %\caption{Hood\footnote{\url{https://en.wikipedia.org/wiki/Naser_Jason_Abdo#Arrest}}\footnote{\url{https://en.wikipedia.org/wiki/Fort_Hood#2011_attack_plot}}}
        \label{fig:hood}
\end{figure}

@@

\section{Related Works}
\label{sec:relatedWorks}
\textbf{Event Detection.} According to how much data are used, the approaches are divided into two groups: the detection \textit{without extra information}, and the detection by \textit{leveraging extra information}.

Most existing methods are implemented \textit{without extra information}.
They utilize the bursty pattern in the text stream to detect events, and are carried out by  clustering articles\cite{Allan:2000wu,Petrovic:2010uj,Wurzer:2015wq}, analyzing word frequencies\cite{Mathioudakis:2010fc,Weng:2011wz}, or finding bursty topics\cite{Diao:2012wj,Yan:2015wm}. 
(1) By clustering articles, UMass\cite{Allan:2000wu}, LSH\cite{Petrovic:2010uj}, k-Term-FSD\cite{Wurzer:2015wq} and other similar methods model the occurred events as clusters of articles, and link the incoming article with an already existed event cluster or label it as the first story of a new event.
The decision is based on whether the dissimilarity between the incoming article and existed event clusters is over the user-specified threshold. 
Taking LSH as an example, as \cite{Petrovic:2010uj} discussed, the threshold controls the result: the big one leads to very few and broad clusters, while the small one results in very small and specific clusters.
Even after carefully set the appropriate threshold, the clusters generated by this kind method are still mixed of events and non-events due to large portion of non-event microblogs, which requires some post-processing methods as the supplement. 
(2) By analyzing word frequencies, TwitterMonitor\cite{Mathioudakis:2010fc} models the bursty words by queueing theory, and EDCoW\cite{Weng:2011wz} exploits wavelet transformation, which converts signal from time domain to time-scale domain, to detect the change point of word signal. 
However they treat the word as the most basic unit in analysis, without regarding how many concepts are represented by the word.
(3) By finding bursty topics, TimeUserLDA, BurstyBTM needs the appropriate number of topics to run the topic modelling, and detects the ``large" events that associate with many articles but ignores the ``small" ones.
